%!TEX root = index.tex

%Entradas do glossário
\newglossaryentry{eclipse}
{
  name=Eclipse,
  description={-- Environnement de développement intégré multi-langage comprenant un espace de travail de base et une extensible système plug-in de personnalisation de l'environnement. Écrit en Java, il peut être utilisé pour développer des applications en Java et d'autres langages de programmation}
}

\newglossaryentry{jee}
{
  name=Java EE,
  description={-- La plate-forme informatique Java d'Oracle destinée aux entreprises. La plate-forme fournit une API et un environnement d'exécution pour l'élaboration et la mise en œuvre du logiciel d'entreprise, y compris les services de réseau et web, et d'autres applications de réseau à grande échelle, multi-niveaux, évolutive, fiable et sécurisée.}
}

\newglossaryentry{SGBD}
{
  name=SGBD,
  description={-- Système de Gestion de Base de Données, est un logiciel système destiné à stocker et à partager des informations dans une base de données, en garantissant la qualité, la pérennité et la confidentialité des informations, tout en cachant la complexité des opérations.}
}

\newglossaryentry{ERP}
{
  name=ERP,
  description={-- De l'anglais \textit{Entreprise Ressource Planning}, est un progiciel qui intègre les principales composantes fonctionnelles de l'entreprise: gestion de production, gestion commerciale, logistique, ressources humaines, comptabilité, contrôle de gestion. À l'aide de ce système unifié, les utilisateurs de différents métiers travaillent dans un environnement applicatif identique qui repose sur une base de données unique. }
}

\newglossaryentry{Better-Place}
{
  name=Better Place,
  description={-- An international company that developed and sold battery-switching battery for electric cars. The corporation did not succeed mainly because of non-standardization of battery models, and has declared bankruptcy in Israel and has initiated the proceedings in Denmark},
}


\newglossaryentry{frunk}
{
  name=frunk,
  description={-- The front trunk. Electric vehicles are usually able to have both rear and front trunks because the batteries are located in the floor, and the motor between the drive wheels},
}

\newglossaryentry{hybrid}
{
	name=hybrid car,
	description={-- Vehicle that uses more than one power source to move the wheels. Most commonly, it refers to hybrid electric vehicles, which combine internal combustion engines and electric motors}
}

\newglossaryentry{li-ion}
{
	name=lithium-ion battery,
	description={-- A rechargeable battery used to power electric vehicles. Li-ion batteries have high energy density and slow self-discharge when not in use, and are known for being more expensive than older nickel metal batteries},
	plural=lithium-ion batteries
}

\newglossaryentry{range-extender}
{
	name=range extender,
	description={-- A system used in hybrid cars where the internal combustion engine is used solely to charge up the battery, and not to power the wheels. This system is used as an emergency tool, when battery is running out of charge},
	plural=range extenders
}

\newglossaryentry{range-anxiety}
{
	name=range anxiety,
	description={-- An expression used to designate a driver's worry that his vehicle won't reach its destination on the current charge, especially because of battery charge restrictions and limited electric power stations on the way}
}

\newglossaryentry{zero-emission}
{
	name=zero-emission vehicle,
	description={-- A vehicle that has zero gas emissions at the tailpipe. Emissions from the manufacturing process are whatsoever ignored in this definition},
	plural=zero tailpipe emissions
}

\newglossaryentry{gas-emission}
{
	name=greenhouse gas,
	description={-- Gas substance (such as water vapor or carbon dioxide) that absorb part of the infrared radiation emitted by the surface of Earth. This process decreases heat loss, keeping the planet warm. Human activities such as industrial or tailpipe emissions increase greenhouse gases concentration on air, changing Earth's average temperature},
	plural=greenhouse gas emissions
}

\newglossaryentry{fuel-cell}
{
	name=fuel cell,
	description={-- Device capable of converting chemical energy into electricity. An electrolyte initiates a chemical reaction that generates electric power when fuel and oxidants, such as hydrogen and oxygen, flow into it. While no greenhouse gases are produced in the process, hydrogen production and distribution may have a significant environmental impact}
}

\newglossaryentry{government-incentives}
{
	name=government incentives,
	description={-- Subsidies or government policies beneficial for electric cars, which vary with federal government and vehicle model. Most incentives are tax credits and personal income tax deduction for costumers},
	plural=government policy
}

\newglossaryentry{bev}
{
	name=battery electric vehicle,
	description={-- Also referred to as all-electric vehicle, it is a vehicle that is use a battery as the only mean to store electricity needed to power the motor},
	plural=battery electric vehicles
}

